---
output: md_document
---

```{r, include=FALSE}
library("printr")
```

This package simply re-packages the supplementary materials (data and code) for **[Quantitative Social Science: An Introduction](http://press.princeton.edu/titles/11025.html)**, available a [kosukeimai/qss](https://github.com/kosukeimai/qss) as an R package.

# Install

**qss** is not available from CRAN, install the version from github with:
```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("jrnold/qss-data")
```

# Usage

The QSS package contains the following datasets:
```{r}
data(package = "qss")
```


The Federalist papers text files are in the `extdata/federalist` directory of the installed package.
```{r}
library("tm")
federalist_dir <- system.file("extdata", "federalist", package = "qss")
dir(federalist_dir)
corpus.raw <- Corpus(DirSource(federalist_dir))
corpus.raw
```

Scripts with the full R code for each chapter are available with `demo`:
```{r}
demo(package = "qss")
```

In 1.3.5 "Data Files", several types of data files are discussed.
These are included in `extdata/`
```{r}
library("foreign")
dir(system.file("extdata", "data_files", package = "qss"))
load(system.file("extdata", "data_files", "UNpop.RData", package = "qss"))
read.csv(system.file("extdata", "data_files", "UNpop.csv", package = "qss"))
read.dta(system.file("extdata", "data_files", "UNpop.dta", package = "qss"))
```

# Build Package

